\documentclass[12pt]{article}
\usepackage{hyperref}
\title{Bio. notes}
\author{Pierre Lindenbaum PhD.}
\date{\today}

\begin{document}
\maketitle
\section{NGS}
\paragraph{http://www.youtube.com/watch?v=HIfI7F3f82A}:\\

exome sequencing may only work 30/40\% of the time\\
genes missing in capture, microRNA, CNV\\
people in dbSNP can be affected.\\
DNA from patients with cardiac rythm disorders (26:07) \\
NOTCH2 cited at (28:51)\\

\paragraph{http://www.youtube.com/watch?v=teTgPIY4LS8}:\\

data integration with array SNP.
PennCNV: copy number variation detection http://www.openbioinformatics.org/penncnv/\\
Sift/polyhpen useful for ordering a large list of variant but not for a single one (28:22)/ \\
http://www.nature.com/ng/journal/v43/n8/full/ng.883.html : gene missing in capture for exome sequecing.\\

\paragraph{samtools mpileup with multiple bam}
From the samtools mailing list: I've recently worked with two pools of samples where I wanted to find SNPs that differentiate the two pools.  I supplied both sample1.bam and sample2.bam to the mpileup command and then bcftools pair calling.  SNPs are called using the combination of the two pools and the resulting vcf file will show genotypes for each sample and a "CLR" value that represents the likelihood that the genotypes are different between the samples.

\paragraph{BGI}
BGI : 167 DNA sequencers producing the equivalent of 2,000 human genomes a day. ( http://www.nytimes.com/2011/12/01/business/dna-sequencing-caught-in-deluge-of-data.html?_r=1) 
BGI churns out so much data that it often cannot transmit its results to clients or collaborators over the Internet or other communications lines because that would take weeks. Instead, it sends computer disks containing the data, via FedEx. 

\section{Definitions:}
\paragraph{phenocopy}: A phenocopy is an individual whose phenotype under a particular environmental condition, is identical to the one of another individual whose phenotype is determined by the genotype.
\paragraph{somatic mutation}: occur after conception, can occur in any of the cells of the body except the germ cells , not passed on to children.
\end{document}
